%-------------------------
% Resume in Latex
% Author : Keenan Schott
% Based off of: https://github.com/jmshima01/LaTeX-Resume-Template
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\uwSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} -- {\small #2} & {\small #3} \\
      {\small #4} & {\small #5} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\minesSubheading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} -- {\small #2} & {\small #3} \\
      {\small #4} & {\small #5} \\
      {\small #6}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
      {\small #3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small{\textbf{#1}} & \small{#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\begin{center}
    \textbf{\huge \scshape Keenan Schott} \\ \vspace{1pt}
    \href{mailto:kschott@uw.edu}{{kschott@uw.edu}} $|$  
    \href{https://keenanschott.com/portfolio/}{{keenanschott.com}} $|$
    \small Seattle, WA $|$
    \small 206-475-6068 
\end{center}

% -------------EDU-------------------
\section{Education}
  \resumeSubHeadingListStart
      \uwSubheading
      {University of Washington}{M.S. in Information Management}{Sep 2024 -- Jun 2025}
      {Program/Product Management \& Consulting (PPMC) Specialization}{GPA: 4.00}
      \minesSubheading
      {Colorado School of Mines}{B.S. in Computer Science}{Aug 2021 -- May 2024}
      {Computer Engineering Specialization}{GPA: 3.94}
      {Summa Cum Laude, Dean's List x6, \href{https://keenanschott.com/portfolio/certificate.pdf}{{Cyber Defense Education Certificate}}}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer Intern}{May 2024 -- Aug 2024}
      {ICR, Inc.}{Louisville, CO}
      \resumeItemListStart
        \resumeItem
        {Built a Request for Information (RFI) web application for a gov. client using React and TypeScript.}
        \resumeItem
        {Enhanced data querying efficiency by \textbf{18\%} through caching and query keys with TanStack.}
        \resumeItem
        {Developed an AI autocompletion tool using ICR’s internal LLM, reducing RFI completion time by \textbf{10\%}.}
        \resumeItem
        {Designed RFI data visualizations using Elasticsearch and Recharts for improved data analysis.}
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineer Intern}{May 2023 -- Apr 2024}
      {Datava}{Westminster, CO}
      \resumeItemListStart
        \resumeItem
        {Optimized query processing and system performance for \textbf{200+} credit unions across the Western U.S.}
        \resumeItem
        {Created API endpoints in PHP using PDO to process, sanitize, and translate user input into PostgreSQL queries.}
        \resumeItem
        {Led development of \textbf{30+} JavaScript components to introduce support for PostgreSQL-specific features.}
        \resumeItem
        {Automated API documentation using Swagger for improved maintainability and developer onboarding.}
      \resumeItemListEnd
    \resumeSubheading
      {Teaching Assistant}{Dec 2021 -- Dec 2023}
      {CS@Mines}{Golden, CO}
      \resumeItemListStart
        \resumeItem
        {Managed \textbf{300+} students over four semesters as a TA, teaching Python and software basics.}
        \resumeItem
        {Assisted in transitioning CSCI 102 to CSCI 128, focusing on computer science's societal impact.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------RESEARCH-----------
\section{Research}
    \resumeSubHeadingListStart
      \resumeSubheading
      {Research Assistant}{Oct 2022 -- Mar 2023}
      {Mines Interactive Robotics Research Lab}{Golden, CO}
          \resumeItemListStart
            \resumeItem
            {Researched perceptions of robot pointing gestures, published at the \href{https://doi.org/10.1145/3610977.3634924}{\textbf{2024 ACM/IEEE HRI Conference}}.}
            \resumeItem{Used R to analyze data from experiments with human participants interacting with robots and virtual reality.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
          \resumeProjectHeading
          {\href{https://keenanschott.com/portfolio/\#project-arbitragecalculatorus}{arbitragecalculatorus.com}}{May 2023 -- Jan 2025}
          \resumeItemListStart
            \resumeItem{Constructed a web app using HTML, CSS, and JavaScript that integrates with a real-time API and implements data parsing and filtering logic to display profitable arbitrage opportunities across U.S.-based online marketplaces.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://keenanschott.com/portfolio/\#project-hspc}{Mines High School Programming Competition}}{Jan 2024 -- Apr 2024}
          \resumeItemListStart
            \resumeItem{Formulated a \href{https://mines-hspc.kattis.com/contests/mines-hspc24/problems/nostragglers}{programming problem} for the annual competition; authored the problem statement in \LaTeX, designed and validated test inputs using Python, developed model solutions, and volunteered in person.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://keenanschott.com/portfolio/\#project-clue}{Clue}}{Jan 2023 -- Jun 2023}
          \resumeItemListStart
            \resumeItem{Redesigned the classic game Clue as part of the CSCI 306 course, showcasing software engineering skills through advanced object-oriented programming principles and comprehensive unit testing in Java.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://keenanschott.com/portfolio/\#project-svd}{Singular Value Decomposition Image Compression}}{Apr 2023}
          \resumeItemListStart
            \resumeItem{Applied Singular Value Decomposition (SVD) to efficiently compress images while preserving key visual information, using Python's robust libraries to display the original image, compression ratio, and retained data.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C, C++, Java, Rust, Go, OCaml, Bash, SQL, R, TypeScript, PHP, HTML, CSS/SCSS} \\
     \textbf{Technologies \& Frameworks}{: React, Node.js, JUnit, NumPy, PostgreSQL, MongoDB, Swagger, MUI, TanStack} \\
     \textbf{Tools \& Platforms}{: Git, Linux, Docker, Jenkins, CI/CD, Wireshark, Jira, UML, Unit Testing, Microcontrollers}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}